Methodology for Assessing the State of the Practice for Domain X

### 2021-10-20 StateOfPractice/Methodology/Methodology.tex
Revised intro paragraph to Section 12 (Estimate of Time Required)

estimate the time required in person hours.  Add a table.  Assume reviewed
material, using provided spreadsheets and AHP tool.  Assume domain has been
identified and domain expert engaged.  Following steps given in
Section~\ref{StepsAQDS}.

>>>>

Table~\ref{TabPersonHours} estimates the time required (in person hours) to
complete a state of the practice assessment for domain X.  The table assumes
that the domain has already been decided and the domain expert has been
recruited.  The table follows the steps outlined in Section~\ref{StepsAQDS}.
Time is not included for reviewing the methodology. Moreover, it is assumed that
the template spreadsheets linked in this document, and the developed AHP tool,
will be employed, rather than developing new tools.  The person hours given are
a rough estimate, based on our experience completing assessments for medical
image analysis software \citep{Dong2021} and for Lattice Boltzmann Method (LBM)
software \citep{Michalski2021}.  These two domains were assessed at the same
time as designing the methodology presented in this document.  We did our best
to estimate the time spent on measurement and separate it from the time spend on
design and development.  The estimate assumes 30 software packages will be
measured; the numbers will need to be adjusted if the total packages changes.
